% TEMPLATE FOR STANDARD QUIZ
% by laura

\documentclass[11pt,epsfig]{article}

\oddsidemargin=0in
\evensidemargin=0in
\textwidth=6.3in
\topmargin=-0.5in
\textheight=9in

\parindent=0in
\pagestyle{empty}

\input{notestpoints}

\begin{document}


%%%(change to appropriate class and semester)
CIS 2033 Fall 2015: Computational Prob and Stat

%%%(change to appropriate quiz type and date)
Quiz 1(Chapter 2) \hspace{2.0in} {Name:} {\underline {\hspace{2.0in}}}
\vspace{2pc}

%%%(modify rules, time, points as appropriate)
Show all work clearly and in order, and circle your final answers.  
Justify your answers algebraically whenever possible; you can use 
your calculator if needed.  You have 10 minutes to take this quiz.
\vspace{2pc}

% problem
\begin{problem}{1}  If an event is certain to happen it has a probability of zero. \\
\hspace{0.5in} A) True \\
\hspace{0.5in} B) False
\end{problem}

% problem
\begin{problem}{10} What is more likely to happen? \\
\hspace{0.5in} A) Rolling a dice and getting a 6 \\
\hspace{0.5in} B) Tossing a coin and getting 'heads'
\end{problem}

% problem
\begin{problem}{10} How many possible outcomes are there when you toss a coin?  (fair coin)\\
\hspace{0.5in} A) 1 \\
\hspace{0.5in} B) 2
\end{problem}

\begin{problem}{10} How many possible outcomes are there when you toss 3 coins simultaneously? (fair coin)\\
\hspace{0.5in} A) 3 \\
\hspace{0.5in} B) 8
\end{problem}

\begin{problem}{10} How many possible outcomes are there when you toss n coins simultaneously? (fair coin)\\
\hspace{0.5in} A) n\\
\hspace{0.5in} B) $2^n$
\end{problem}

\begin{problem}{10} How many possible outcomes are there when you toss 1 coin for n times? (fair coin)\\
\hspace{0.5in} A) n\\
\hspace{0.5in} B) $2^n$
\end{problem}

\begin{problem}{10} What's the probability of all heads, when you toss 1 coin for n times? (fair coin)\\
\hspace{0.5in} A) $1/n$\\
\hspace{0.5in} B) $(1/2)^n$
\end{problem}

\end{document}